A Roadmap for\\HEP Software and Computing R\&D\\for the 2020s

### 2018-11-06 CWP/papers/HSF-CWP-2017-01_roadmap/latex/cwp-main.tex
Add WG references

\begin{itemize}
\item
  Understand better the relationship between the performance and costs
  of the WLCG system, and how it delivers the necessary functionality to
  support LHC physics. This will be an ongoing process, started by the
  recently formed System Performance and Cost Modeling Working Group,
  and aims to provide a quantitative assessment for any proposed
  changes.
\item
  Define the functionality needed to implement a federated data centre
  concept (``data lake'') that aims to reduce the operational cost of
  storage for HL-LHC, and at the same time better manage network
  capacity, whilst maintaining the overall CPU efficiency. This would
  include the necessary qualities of service, and options for regionally
  distributed implementations, including the ability to flexibly respond
  to model changes in the balance between disk and tape. This work
  should be done in conjunction with the existing Data Organisation,
  Management and Access Working Group to evaluate the impact of the
  different access patterns and data organisations envisaged.
\item
  Building upon the experience of projects currently exploring SDN
  potential, define the role for this technology in managing data transfers and
  access and the integration strategy into experiment frameworks.
\item
  Establish an agreement on the common data management functionality
  that is required by experiments, targeting a consolidation and a lower
  maintenance burden. The intimate relationship between the management
  of elements in storage systems and metadata must be recognised. This
  work requires coordination with the Data Processing Frameworks
  Working Group. It
  needs to address at least the following use cases:

  \begin{itemize}
  \item
    processing sites that may have some small disk cache, but do not
    manage primary data;
  \item
    fine grained processing strategies that may enable processing of
    small chunks of data, with appropriate bookkeeping support;
  \item
    integration of heterogeneous processing resources, such as HPCs and
    clou\-ds.
  \end{itemize}
\item
  Explore scalable and uniform means of workload scheduling, which
  incorporate dynamic heterogenous resources, and the capabilities of
  finer grained processing that increases overall efficiency. The
  optimal scheduling of special workloads that require particular
  resources is clearly required.
\item
  Contribute to the prototyping and evaluation of a quasi-interactive
  analysis facility that would offer a different model for physics
  analysis, but would also need to be integrated into the data and
  workload management of the experiments. This is work to be done in
  collaboration with the Data Analysis and Interpretation Working Group.
\end{itemize}

>>>>

\begin{itemize}
\item
  Understand better the relationship between the performance and costs
  of the WLCG system, and how it delivers the necessary functionality to
  support LHC physics. This will be an ongoing process, started by the
  recently formed System Performance and Cost Modeling Working Group~\cite{SPCMWG},
  and aims to provide a quantitative assessment for any proposed
  changes.
\item
  Define the functionality needed to implement a federated data centre
  concept (``data lake'') that aims to reduce the operational cost of
  storage for HL-LHC, and at the same time better manage network
  capacity, whilst maintaining the overall CPU efficiency. This would
  include the necessary qualities of service, and options for regionally
  distributed implementations, including the ability to flexibly respond
  to model changes in the balance between disk and tape. This work
  should be done in conjunction with the existing Data Organisation,
  Management and Access Working Group~\cite{WLCG-DOMA} to evaluate the impact of the
  different access patterns and data organisations envisaged.
\item
  Building upon the experience of projects currently exploring SDN
  potential, define the role for this technology in managing data transfers and
  access and the integration strategy into experiment frameworks.
\item
  Establish an agreement on the common data management functionality
  that is required by experiments, targeting a consolidation and a lower
  maintenance burden. The intimate relationship between the management
  of elements in storage systems and metadata must be recognised. This
  work requires coordination with the Data Processing Frameworks
  Working Group. It
  needs to address at least the following use cases:

  \begin{itemize}
  \item
    processing sites that may have some small disk cache, but do not
    manage primary data;
  \item
    fine grained processing strategies that may enable processing of
    small chunks of data, with appropriate bookkeeping support;
  \item
    integration of heterogeneous processing resources, such as HPCs and
    clou\-ds.
  \end{itemize}
\item
  Explore scalable and uniform means of workload scheduling, which
  incorporate dynamic heterogenous resources, and the capabilities of
  finer grained processing that increases overall efficiency. The
  optimal scheduling of special workloads that require particular
  resources is clearly required.
\item
  Contribute to the prototyping and evaluation of a quasi-interactive
  analysis facility that would offer a different model for physics
  analysis, but would also need to be integrated into the data and
  workload management of the experiments. This is work to be done in
  collaboration with groups working on new data analysis models.
\end{itemize}
